---
title: 'Data download "More Unequal or Not as Rich: Revisting the Latin American exception"'
author: "Mauricio de Rosa, Ignacio Flores and Marc Morgan"
---

Welcome to the data download page for [More Unequal or Not as Rich? Revisiting the Latin American Exception](https://osf.io/preprints/socarxiv/akq89/). The paper examines the income distribution in Latin America and challenges the commonly held belief that the region is an exception to global trends of rising inequality. To address this question, we built the most comprehensive database to date, which accounts for 80% of the region's population and combines harmonized surveys, social security data, income tax declarations, and national accounts. As a result, we are making available four documents for download. Our estimates cover the period 2000-2020. To download everything at once click [here](data/more_unequal_or_not_as_rich_fulldata.zip)


```{r, include=FALSE, echo=FALSE}
library(DT)
library(magrittr)
library(tidyverse)
library(readxl)

# Load data
detailed <- read.csv("data/smicrofile_long_detailed_sep2022.csv") %>% 
  filter(country == "BRA" & year == 2020)
abrev <- read_excel("data/abreviaciones_esp.xlsx")
#data_v2 <- read.csv("data/smicrofile_long_efftax_sep2022.csv")
#data_v3 <- read.csv("data/smicrofile_long_grouped_sep_2022.csv")
```


1. **Code Dictionary:** This document associates acronyms and codes to full descriptions in English, which will help you understand the variables used in the other data files. Only the Spanish version is available for now.

2. **Detailed income composition:** This data set provides detailed estimates on income levels and composition at the percentile level, for every country, every year, and every step of our adjustment process (from the raw survey to the full imputation of macroeconomic aggregates). This data set will allow you to conduct your own analyses and explore the findings of the paper in more detail.

3. **Grouped inequality estimates:** This data set provides grouped estimates such as the Gini coefficients, the top 1% share, the bottom 50%, and more. This data set is useful if you are interested in the overall trends of income inequality in the region.

4. **Effective Tax Rates:** This data set displays effective tax rates and their composition at the percentile level. Effective tax rates are estimated with respect to unimputed pre-tax income. This data set will allow you to examine the impact of taxes and transfers on income distribution in the region, as well as their progressivity over 2000-2021.

Below you will find a preview of this documents, also allowing you to download them one by one. 

# Preview of synthetic microfiles {.tabset}

## Code dictionary

```{r, echo=FALSE}
datatable(abrev, rownames = F)
```

## Detailed income composition

coming soon

## Grouped inequality estimates

coming soon

```{r, include=FALSE, echo=FALSE}
#datatable(detailed, width = 600) %>%
  #formatRound(c("year", "average", "thr", "avg", "topavg"), digits = 0) %>% 
  #formatPercentage(c("gini", "bckt_sh", "topsh", "b"), digits = 1)
```

## Effective tax rates 

coming soon
